Final Workflow for CLM5 paper

### 2018-11-05 SIfigs.tex
Updates from ShareLaTeX

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_GPP.png}
     \caption{GPP CO2 and N respones}
     \label{GPP CO2 and N respones}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_NPP.png}
     \caption{NPP CO2 and N respones}
     \label{NPP CO2 and N respones}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_LAI.png}
     \caption{LAI CO2 and N respones}
     \label{LAI CO2 and N respones}
  \end{figure}

>>>>

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/OCT_CNdep_GPP1_CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p2006.png}
     \caption{GPP CO2 and N respones}
     \label{GPP CO2 and N respones}
  \end{figure}

\begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/OCT_CNdep_TOTVEGC1_CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p2006.png}
     \caption{Total vegetation carbon CO2 and N respones}
     \label{Total vegetation carbon CO2 and N respones}
  \end{figure}
